Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-29 main_paper.tex
Tweak wording in 'thanks'

\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{%
  All authors: Department of Economics, Iowa State University.
  260 Heady Hall, Ames, IA 50011.
  Bartalotti: \protect\url{bartalot@iastate.edu};
  Calhoun: \protect\url{gcalhoun@iastate.edu} and
  \protect\url{http://gray.clhn.org};
  He: \protect\url{yanghe@iastate.edu}. Source code for the Monte Carlo
  experiments and empirical component of this paper are available online
  at \protect\url{https://github.com/grayclhn/boot-rd}. We would like to
  thank Matias Cattaneo, Juan Carlos Escanciano, Sebastian Calonico, Max Farrell, Helle Bunzel, Brent Kreider, Quentin Brummet, seminar participants at
  the Advances in Econometrics conference on Regression Discontinuity
  Designs, Third Annual Conference of the International Association for Applied Econometrics,
 2016 North American Summer Meeting of the Econometric Society and the $69^{th}$ European Meeting of the Econometric Society, and especially the two anonymous referees for   substantive help and advice on earlier versions of this paper.}}

>>>>

\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{%
  All authors: Department of Economics, Iowa State University.
  260 Heady Hall, Ames, IA 50011.
  Bartalotti: \protect\url{bartalot@iastate.edu};
  Calhoun: \protect\url{gcalhoun@iastate.edu} and
  \protect\url{http://gray.clhn.org};
  He: \protect\url{yanghe@iastate.edu}. Source code for the Monte Carlo
  experiments and empirical component of this paper are available online
  at \protect\url{https://github.com/grayclhn/boot-rd}. We would like to
  thank Matias Cattaneo, Juan Carlos Escanciano, Sebastian Calonico, Max Farrell, Helle Bunzel, Brent Kreider, Quentin Brummet, seminar participants at
  the Advances in Econometrics conference on Regression Discontinuity
  Designs, Third Annual Conference of the International Association for Applied Econometrics,
 2016 North American Summer Meeting of the Econometric Society and the $69^{th}$ European Meeting of the Econometric Society, and especially the two anonymous referees for
  substantial help and advice on earlier versions of this paper.}}
